#my project

#load libraries

```{r, message=FALSE, warning=FALSE}


load.libraries <- c('tidyverse', 'gridExtra', 'dplyr', 'lubridate', 'ggplot2', 'stringr', 'randomForest', 'fastDummies', 'janitor', 'caret', 'AUC', 'plotrix')
install.lib <- load.libraries[!load.libraries %in% installed.packages()]
for(libs in install.lib) install.packages(libs, dependences = TRUE)
sapply(load.libraries, require, character = TRUE)

```
#import data   
   
   
```{r, message=FALSE, warning=FALSE}

orders_data <- read.csv(file = "orders_data.csv") 

```


#make data anonymous 

```{r, message=FALSE, warning=FALSE}

Id <- unique(orders_data$buyer)

names(Id) <- c(1:length(Id))

Id_Conversion <- data.frame(buyer = Id, Person = names(Id))

orders_data <- merge(orders_data, Id_Conversion, by = "buyer") %>%
  subset(select = -buyer) %>%
  mutate("buyer" = as.character(Person)) %>%
  subset(select = -Person) 

```

#preview the data

```{r, message=FALSE, warning=FALSE}
dim(orders_data)



length(unique(orders_data$order_no))
```
#preview the data
  
```{r, message=FALSE, warning=FALSE}
colnames(orders_data)

#view a selection of the data
str(orders_data[1,c("sku", "ship_city", "item_total", "order_date", "description")])
```

#clean the data and feature engineering

```{r, message=FALSE, warning=FALSE}

#tidying all variables, and splitting order_date variable

orders_data <- orders_data %>% 
   mutate(ship_city = substr(ship_city, 1, nchar(ship_city)-1)) %>%
   mutate(shipping_fee   = as.double(gsub(",", "",(substr(shipping_fee, 4, nchar(shipping_fee)))))) %>% 
   mutate(item_total =   as.double(gsub(",", "",(substr(item_total, 4, nchar(item_total)))))) %>% 
   mutate(sku = substr(sku, 7,   nchar(sku))) %>% 
   mutate(day = substr(order_date, 1, 3)) %>%  
   mutate(order_time = substr(order_date, 19, nchar(order_date)-3)) %>%
   mutate(order_hour = hour(mdy_hm(paste("11/11/99", order_time, sep =" ")))) %>% 
   mutate(order_minute = minute(mdy_hm(paste("11/11/99", order_time, sep =" ")))) %>% 
   mutate(timezone = substr(order_date, nchar(order_date)-3, nchar(order_date))) %>% 
   mutate(order_date1 = substr(order_date, 6, 18)) %>% 
   mutate(order_date = dmy(substr(order_date, 6, 18))) %>% 
   mutate(ship_city = tolower(trimws(ship_city, which = "both"))) %>%
   mutate(ship_state = tolower(trimws(ship_state, which = "both"))) %>%
   mutate(description = tolower(trimws(description, which = "both"))) %>% 
   mutate(quantity = as.double((quantity)))



orders_data[is.na(orders_data$order_date), 'order_date'] <- 
  dmy(paste(substring(orders_data[is.na(orders_data$order_date), 'order_date1'], 1, 6), substring(orders_data[is.na(orders_data$order_date), 'order_date1'], 10, 13), sep=" "))

orders_data <- orders_data %>%
  subset(select = -c(order_date1, day, order_time))





#correcting one-off cities and states

orders_data[orders_data$ship_city == as.character("mumbai 400 026"), c("ship_city")] <- as.character("mumbai")

orders_data[orders_data$ship_city == as.character("navi mumbai"), c("ship_city")] <- as.character("mumbai")

orders_data[orders_data$ship_city == as.character("thane district"), c("ship_city")] <- as.character("thane")

orders_data[orders_data$ship_city == as.character("kodambakkam, chennai"), c("ship_city")] <- as.character("chennai")

orders_data[orders_data$ship_state == as.character("mohali,"), c("ship_state")] <- as.character("mohali")

orders_data[orders_data$ship_state == as.character("chandigarh,"), c("ship_state")] <- as.character("chandigarh")

#Feature engineering by tracking key words in description

orders_data <- orders_data %>%
  mutate(gender = 
           ifelse(str_detect(orders_data$description, 'women') | str_detect(orders_data$description, 'woman'), as.character('women'),
                  ifelse(str_detect(orders_data$description, ' men') | str_detect(orders_data$description, ' man')| str_detect(orders_data$description, ' gent'), as.character('men'),
                         ifelse(str_detect(orders_data$description, 'kid'), as.character('kid'), as.character('none')))))




#Tracking other key words in descriptions for more feature engineering
#assessories <- lipstick, jewelry box 
#bags <- bag, purse, 
#banks <- bank
#wallet <-wallet


orders_data <- orders_data %>%
  mutate(item_type = 
           ifelse(str_detect(orders_data$description, 'lipstick') | str_detect(orders_data$description, 'jewelry'), as.character('accessories'),
                  ifelse(str_detect(orders_data$description, 'bag') | str_detect(orders_data$description, 'purse'), as.character('bags'),
                         ifelse(str_detect(orders_data$description, 'bank'), as.character('banks'),
                                ifelse(str_detect(orders_data$description, 'wallet'), as.character('wallets'), as.character('none'))))))




#cleaing up one-off descriptions

orders_data$description[28] <- as.character('bright and colorful handmade shantiniketan leather ganesh ji piggy coin bank for kids/adults | home decor handicrafts (black)')

orders_data$description[80] <- as.character('bright and colorful handmade shantiniketan leather ganesh ji piggy coin bank for kids/adults | home decor handicrafts (yellow)')

orders_data$description[105] <- as.character('bright and colorful handmade shantiniketan leather ganesh ji piggy coin bank for kids/adults | home decor handicrafts (blue)')

orders_data$description[124] <-as.character('bright and colorful handmade shantiniketan leather ganesh ji piggy coin bank for kids/adults | home decor handicrafts (green)') 

orders_data$description[143] <-  as.character('bright and colorful handmade shantiniketan leather ganesh ji piggy coin bank for kids/adults | home decor handicrafts (black)')

#splitting description by deliminator into more variables

orders_data <- orders_data %>% 
  mutate(description.1 = 
           trimws(vapply(str_split(description, "\\|"), '[', 1, FUN.VALUE = character(1)), which="both")) %>% 
  mutate(description.2 = 
           trimws(vapply(str_split(description, "\\|"), '[', 2, FUN.VALUE = character(1)), which="both")) %>% 
  mutate(description.3 = 
           trimws(vapply(str_split(description, "\\|"), '[', 3, FUN.VALUE = character(1)), which="both")) %>% 
  mutate(description.4 = trimws(vapply(str_split(description, "\\|"), '[', 4, FUN.VALUE = character(1)), which="both"))

orders_data[, c("description.1", "description.2", "description.3", "description.4")] <- orders_data %>% 
  summarise(description.1 = ifelse(is.na(description.1), as.character("none"), description.1), description.2 = ifelse(is.na(description.2), as.character("none"), description.2), description.3 = ifelse(is.na(description.3), as.character("none"), description.3), description.4 = ifelse(is.na(description.4), as.character("none"), description.4))

#revalue function
my_revalue <- function(x, ...){
  reval <- list(...)

  from <- names(reval)
  to <- unlist(reval)

  out <- eval(parse(text= paste0("{", paste0(paste0("x[x ==", "'", from,"'", "]", "<-", "'", to, "'"), collapse= ";"), ";x", "}")))

  return(out)
}

#feature engineering order months and time of day

orders_data <- orders_data %>%
  mutate(month = as.integer(month(order_date)))


#order month
orders_data$month <- my_revalue(orders_data$month, "1"= "01 - January", "2"="02 - February", "3"="03 - March", "4"="04 - April", "5"="05 - May", "6"="06 - June", "7"="07 - July", "8"="08 - August", "9"="09 - September", "10"="10 - October", "11"="11 - November", "12"="12 - December")


#order time of day
orders_data <- orders_data %>% 
  mutate(tod = ifelse(order_hour < 6, as.character('night'), ifelse(order_hour< 12, as.character('morning'), ifelse(order_hour < 18, as.character('afternoon'), as.character('evening') ))))


```


  
   
#see the results  
   
```{r, message=FALSE, warning=FALSE}

colnames(orders_data)

str(orders_data[1, c("sku", "ship_city", "item_total", "order_date", "description.1", "gender", "item_type")])
```






#Imputing the missing data



```{r, message=FALSE, warning=FALSE}

na.cols <- which(colSums(is.na(orders_data)) > 0)


#see the missing data count
orders_data[na.cols] %>% 
  is.na() %>% 
  colSums() %>%
  sort(decreasing = TRUE)

```

#Variables cod, shipping_fee, and item_total have 124, 26 and 18 missing entries respectively    
 
  

  
#Helper functions.

  
```{r, message=FALSE, warning=FALSE}

#getmode function to find modes
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

#function to locate the nulls
getNa <- function(data_in, i) {
  data <- which(is.na(data_in[[i]]))
  return (data)
}

```



  
#imputing null data in variable: item_total
  
```{r, message=FALSE, warning=FALSE}

#completing null item_total values with most common item_total values
#from obersavtions that share the same SKU value

item_total.na <-getNa(orders_data, "item_total")

orders_data[item_total.na, c("sku", "item_total")] <- orders_data %>%   group_by(sku) %>% 
  mutate(item_mode = getmode(item_total)) %>% 
  ungroup() %>% 
  summarise(sku[item_total.na], item_total = item_mode[item_total.na])

paste("There are", length(which(is.na(orders_data$item_total))), "null entries in item_total", sep=" ")



#completing null item_total values with most common item_total values
#from obersavtions that share the same description.1 value

item_total.na <-getNa(orders_data, "item_total")

orders_data[item_total.na, c("description.1", "item_total")] <- orders_data %>% 
  group_by(description.1) %>% 
  mutate(item_mode = getmode(item_total)) %>% 
  ungroup() %>% 
  summarise(description.1[item_total.na], item_total = item_mode[item_total.na])

paste("There are", length(which(is.na(orders_data$item_total))), "null entries in item_total", sep=" ")



#completing null item_total values with most common item_total value

item_total.na <-getNa(orders_data, "item_total")

orders_data[item_total.na, c("item_total")] <- orders_data %>% 
  summarise(item_total = getmode(item_total))


paste("There are", length(which(is.na(orders_data$item_total))), "null entries in item_total", sep=" ")

```


#imputing null data in variable: shipping_fee


```{r, message=FALSE, warning=FALSE}



paste("There are", length(which(is.na(orders_data$shipping_fee))), "null entries in shipping_fee", sep=" ")



#replace NA shipping fee with most common shipping fees when sharing 
# other similar skus and cities variables

shipping_fee.na <- getNa(orders_data, "shipping_fee")

orders_data[shipping_fee.na, c("sku", "shipping_fee", "ship_city")] <- orders_data %>% 
  group_by(sku, ship_city) %>% 
  mutate(item_mode = getmode(shipping_fee)) %>% 
  ungroup() %>% 
  summarise(sku[shipping_fee.na], shipping_fee = item_mode[shipping_fee.na], ship_city = ship_city[shipping_fee.na])

paste("There are", length(which(is.na(orders_data$shipping_fee))), "null entries in shipping_fee", sep=" ")

#replace NA shipping fee with most common shipping fees when sharing 
# other similar skus and ship_states variables

shipping_fee.na <- getNa(orders_data, "shipping_fee")

orders_data[shipping_fee.na, c("sku", "shipping_fee", "ship_state")] <- orders_data %>% 
  group_by(sku, ship_state ) %>% 
  mutate(item_mode = getmode(shipping_fee)) %>% 
  ungroup() %>% 
  summarise(sku[shipping_fee.na], shipping_fee = item_mode[shipping_fee.na], ship_state = ship_state[shipping_fee.na])

paste("There are", length(which(is.na(orders_data$shipping_fee))), "null entries in shipping_fee", sep=" ")


#replace NA shipping fee with most common shipping fees when sharing 
# other matching skus

shipping_fee.na <- getNa(orders_data, "shipping_fee")

orders_data[shipping_fee.na, c("sku", "shipping_fee")] <- orders_data %>% 
  group_by(sku) %>% 
  mutate(item_mode = getmode(shipping_fee)) %>% 
  ungroup() %>% 
  summarise(sku[shipping_fee.na], shipping_fee = item_mode[shipping_fee.na])


paste("There are", length(which(is.na(orders_data$shipping_fee))), "null entries in shipping_fee", sep=" ")



#replace NA shipping fee with most common shipping fees when sharing 
# other matching ship_city variable


shipping_fee.na <- getNa(orders_data, "shipping_fee")

orders_data[shipping_fee.na, c("ship_city", "shipping_fee")] <- orders_data %>% 
  group_by(ship_city) %>% 
  mutate(item_mode = getmode(shipping_fee)) %>% 
  ungroup() %>% 
  summarise(ship_city[shipping_fee.na], shipping_fee = item_mode[shipping_fee.na])


paste("There are", length(which(is.na(orders_data$shipping_fee))), "null entries in shipping_fee", sep=" ")


#replace NA shipping fee with most common shipping fees when sharing 
# other matching ship_state variables

shipping_fee.na <- getNa(orders_data, "shipping_fee")

orders_data[shipping_fee.na, c("ship_state", "shipping_fee")] <- orders_data %>% 
  group_by(ship_state) %>% 
  mutate(item_mode = getmode(shipping_fee)) %>% 
  ungroup() %>% 
  summarise(ship_state[shipping_fee.na], shipping_fee = item_mode[shipping_fee.na])

paste("There are", length(which(is.na(orders_data$shipping_fee))), "null entries in shipping_fee", sep=" ")

```



#imputing null data in variable: cod

```{r, message=FALSE, warning=FALSE}

orders_data$cod[is.na(orders_data$cod)] <- 'Cash in advance'

na.cols <- which(colSums(is.na(orders_data)) > 0)

paste("There are", length(na.cols), "columns with null data")

```

#Helper functions for the plots.

```{r, message=FALSE, warning=FALSE}
 
plotHist <- function(data_in, i) {
  data <- data.frame(x=data_in[[i]])
  p <- ggplot(data=data, aes(x=factor(x))) + stat_count(color="red", fill="red") + xlab(colnames(data_in[i])) + theme_light() + 
      theme(axis.text.x = element_text(angle = 30, hjust =1))
  return (p)
}

plotHist.nolabs <- function(data_in, i) {
  data <- data.frame(x=data_in[[i]])
  p <- ggplot(data=data, aes(x=factor(x))) + stat_count(color="red", fill="red") + xlab(colnames(data_in[i])) + theme_light() + 
      theme(axis.text.x = element_blank())
  return (p)
}

plotHist.ninety <- function(data_in, i) {
  data <- data.frame(x=data_in[[i]])
  p <- ggplot(data=data, aes(x=factor(x))) + stat_count(color="red",  fill="red") + xlab(colnames(data_in[i])) + theme_light() + 
      theme(axis.text.x = element_text(angle = 90, hjust =1))
  return (p)
}
doPlots <- function(data_in, fun, ii, ncol=3) {
  pp <- list()
  for (i in ii) {
    p <- fun(data_in=data_in, i=i)
    pp <- c(pp, list(p))
  }
  do.call("grid.arrange", c(pp, ncol=ncol))
}


```

#Visualize the data.

```{r, message=FALSE, warning=FALSE}
doPlots(orders_data, plotHist.nolabs, c("ship_state", "ship_city", "buyer", "sku", "description", "description.1", "description.2", "order_date"))
```

#Observation(s): There was a popular SKU. Let's look closer.

```{r, message=FALSE, warning=FALSE}
orders_data[c("sku", "description.1", "description.2", "order_no", "quantity")] %>% 
  group_by(sku) %>% 
  summarise(x = sum(quantity), descr = unique(description.1)) %>% 
  arrange(-x) %>% 
  ggplot(aes(x=sku,y=x)) + geom_bar(stat="identity", color="black", fill="red")  +
  labs(title="Total Sales of each SKU",x="SKU", y = "Units sold") +
  theme(axis.text.x = element_text(angle = 90, hjust =1))
```



```{r, message=FALSE, warning=FALSE}

product <- orders_data[c("sku", "description.1", "description.2", "order_no", "quantity")] %>% 
  group_by(sku) %>% 
  mutate(x = sum(quantity)) %>% 
  ungroup() %>%
  filter(x == max(x)) %>% 
  group_by(sku) %>% 
  summarise(description.1 = unique(description.1), description.2 = unique(description.2), x = unique(x))

paste("With a total sold of ", product["x"], ", the most popular product, by far, is SKU:  ", product["sku"], "  Description: ", toupper(product["description.1"]), sep = "")


```


```{r, message=FALSE, warning=FALSE}

doPlots(orders_data, plotHist, c("order_status", "cod", "gender", "quantity", "item_type", "tod"))
```


#Observation(s): Most orders were for only one item. item_type and gender appear to represent the same data. 

```{r, message=FALSE, warning=FALSE}
doPlots(orders_data, plotHist.nolabs, c("shipping_fee", "item_total"))
```


```{r, message=FALSE, warning=FALSE}
orders_data %>%
  group_by(month) %>%
  summarise(Total_Sales = sum(item_total)) %>%
  ggplot(aes(x=month, y=Total_Sales)) + geom_bar(stat="identity", fill = "red", position=position_dodge()) + scale_fill_discrete(name = "", labels = c("Week", "Weekend")) +
labs(title="Busiest Month",x="Month", y = "sales")+
  theme(axis.text.x = element_text(angle = 45, hjust =1))

```


#Observation(s): December makes up an estimated third of the total sales. 



#Visualizing our target variable order_status. 

```{r, message=FALSE, warning=FALSE}
orders_data %>%
  group_by(cod, order_status) %>% 
  summarise(orders = sum(length(unique(order_no)))) %>% 
  ggplot(aes(x=cod, y=orders, fill=order_status)) + geom_bar(stat="identity", position=position_dodge()) + scale_fill_discrete(name = "Order Status", labels = c("Delivered to buyer", "Returned to seller")) +
  labs(title="Payment Method",x="", y = "Order count")+
  theme()


orders_data %>%
  group_by(item_type, order_status) %>% 
  summarise(orders = sum(length(unique(order_no)))) %>% 
  ggplot(aes(x=item_type, y=orders, fill=order_status)) + geom_bar(stat="identity", position=position_dodge()) + scale_fill_discrete(name = "Order Status", labels = c("Delivered to buyer", "Returned to seller")) +
  labs(title="Item Type",x="", y = "Order count")+
  theme()


orders_data %>%
  group_by(tod, order_status) %>% 
  summarise(orders = sum(length(unique(order_no)))) %>% 
  ggplot(aes(x=tod, y=orders, fill=order_status)) + geom_bar(stat="identity", position=position_dodge()) + scale_fill_discrete(name = "Order Status", labels = c("Delivered to buyer", "Returned to seller")) +
  labs(title="Time of Day the Order was Made",x="", y = "Order count")+
  theme()


orders_data %>%
  group_by(month, order_status) %>% 
  summarise(orders = sum(length(unique(order_no)))) %>% 
  ggplot(aes(x=month, y=orders, fill=order_status)) + geom_bar(stat="identity", position=position_dodge()) + scale_fill_discrete(name = "Order Status", labels = c("Delivered to buyer", "Returned to seller")) +
  labs(title="Months and Order Status",x="", y = "Order count")+
  theme(axis.text.x = element_text(angle = 45, hjust =1))




#showing number of canceled orders in different item total buckets


orders_data %>%
  mutate(price = ifelse(orders_data$item_total<300, as.character('0-300'),
                        ifelse( orders_data$item_total<400, as.character('300-400'), 
                                ifelse(orders_data$item_total<500, as.character('400-500'), as.character("above500"))))) %>% 
  group_by(price, order_status) %>% 
  summarise(order_total = sum(length(order_no))) %>% 
  ggplot(aes(x=price, y=order_total, fill=order_status)) + geom_histogram(stat="identity", position=position_dodge()) + scale_fill_discrete(name = "Order Status", labels = c("Delivered to buyer", "Returned to seller")) +
  labs(title="Order Total Price",x="", y = "Order count", caption = "x in INR")+
  theme()

```





#Observation(s): From the tables above, variables cod, item_type, tod, month and item_total all show importance on whether a shipment was accepted or rejected. 





#Pearson's Chi-square test of independence

```{r, message=FALSE, warning=FALSE}

chisq.test(table(orders_data$item_type, orders_data$gender))


chisq.test(table(orders_data$ship_state, orders_data$ship_city))
```

#modeling
  
  
```{r}

classes <- unique(orders_data$order_status)

paste("There are", sum(length(orders_data$order_status)), "total observations. There are only", sum(length(orders_data$order_status[orders_data$order_status != as.character('Delivered to buyer')])), "observations, or", round((sum(length(orders_data$order_status[orders_data$order_status != as.character('Delivered to buyer')])) /  sum(length(orders_data$order_status)) ) * 100, digits = 2), "percent, where the shipments were rejected") 
```

#Choosing the relevant variables.
  
```{r, message=FALSE, warning=FALSE}
df_model <- orders_data[c("order_status", "item_total", "shipping_fee", "ship_city", "item_type", "cod", "month", "tod")]

```

#Change categorical variables to factors.

```{r, message=FALSE, warning=FALSE}

#characters to factors
for(i in 1:ncol(df_model)){
  if (is.character(df_model[,i])){
    df_model[,i] <- as.factor(df_model[,i])
  }
}


```

#Getting dummy data
  
```{r, message=FALSE, warning=FALSE}

# Make dummy variables of two columns:
dataf <- dummy_cols(df_model, select_columns = c("ship_city", "item_type", "cod", "month", "tod"))

dataf <- dataf %>% 
  subset(select = -c(cod, item_type, month, ship_city, tod))

dataf <- clean_names(dataf)

```

#Train/Test split and balancing data.
  
```{r, message=FALSE, warning=FALSE}
set.seed(123)
trainIndex <- createDataPartition(dataf$order_status, p = .7,
                                  list = FALSE,
                                  times = 1)
train <- dataf[ trainIndex,]
test <- dataf[-trainIndex,]

#up sampling data
trainup<-upSample(x=train[,-ncol(train)],
                  y=train$order_status)

testup<-upSample(x=test[,-ncol(test)],
                 y=test$order_status)




trainup <- trainup %>% 
  subset(select = -c(Class))

testup <- testup %>% 
  subset(select = -c(Class))
```

#Random Forest.

```{r, message=FALSE, warning=FALSE}

set.seed(123)
output.forest <- randomForest(order_status~., data = trainup)


# View the forest results.
print(output.forest) 

#make predictions using model
p2 <- predict(output.forest, test)

confusionMatrix(p2, test$order_status)

```




#tune the model
  
  
#find the best mtry value
  
```{r, message=FALSE, warning=FALSE}
#find the best mtry for random forest
mtry <- tuneRF(trainup[-1],trainup$order_status, ntreeTry=500,
               stepFactor=1.5,improve=0.01, trace=TRUE, plot=TRUE)
best.m <- mtry[mtry[, 2] == min(mtry[, 2]), 1]

print(best.m)
```




#optimal maxnodes value


```{r}
#looking for best node max pt 1
store_maxnode <- list()
tuneGrid <- expand.grid(.mtry = best.m)
for (maxnodes in c(5: 15)) {
  set.seed(123)
  rf_maxnode <- train(order_status~.,
                      data = trainup,
                      method = "rf",
                      metric = "Accuracy",
                      tuneGrid = tuneGrid,
                      importance = TRUE,
                      nodesize = best.m,
                      maxnodes = maxnodes,
                      ntree = 500)
  current_iteration <- toString(maxnodes)
  store_maxnode[[current_iteration]] <- rf_maxnode
}
results_mtry <- resamples(store_maxnode)
summary(results_mtry)

#looking for best node max pt 2
store_maxnode <- list()
tuneGrid <- expand.grid(.mtry = best.m)
for (maxnodes in c(15: 30)) {
  set.seed(123)
  rf_maxnode <- train(order_status~.,
                      data = trainup,
                      method = "rf",
                      metric = "Accuracy",
                      tuneGrid = tuneGrid,
                      importance = TRUE,
                      nodesize = best.m,
                      maxnodes = maxnodes,
                      ntree = 500)
  current_iteration <- toString(maxnodes)
  store_maxnode[[current_iteration]] <- rf_maxnode
}
results_mtry <- resamples(store_maxnode)
summary(results_mtry)

```

#number of trees

```{r, message=FALSE, warning=FALSE}

#looking for best number of trees
store_maxtrees <- list()
for (ntree in c(250, 300, 350, 400, 450, 500, 550, 600, 800, 1000, 2000)) {
  set.seed(123)
  rf_maxtrees <- train(order_status~.,
                       data = trainup,
                       method = "rf",
                       metric = "Accuracy",
                       tuneGrid = tuneGrid,
                       importance = TRUE,
                       nodesize = best.m,
                       maxnodes = 21,
                       ntree = ntree)
  key <- toString(ntree)
  store_maxtrees[[key]] <- rf_maxtrees
}
results_tree <- resamples(store_maxtrees)
summary(results_tree)
```


#optimal random forest
  
```{r}
set.seed(123)
output.forest <-randomForest(order_status~.,data=trainup, mtry=best.m , importance = TRUE,  ntree=300, maxnodes = 21)
print(output.forest)


p2 <- predict(output.forest, test)


confusionMatrix(p2, test$order_status)

```



#variable importance

```{r, message=FALSE, warning=FALSE}

varImpPlot(output.forest,
           n.var = 10)
```


